---
title: "Analysis on Gender Statictics"
author: "Hsu, Quintero, Wadhwa"
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: dinat
subtitle: "Team 6- The Outsiders"
header-includes:
- \usepackage{titling}
- \usepackage{float}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Figures/logo.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---

\section*{1}

#1 Janice

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(readr)
library(broom)
library(stringr)
library(patchwork)
library(kableExtra)
library(knitr)
library(bookdown)
library(naniar)
library(GGally)

Genderstatistics <- read_csv("Data/Genderstatistics.csv")%>%
  rename('2011' = '2011 [YR2011]',
         '2012' = '2012 [YR2012]', 
         '2013' = '2013 [YR2013]', 
         '2014' = '2014 [YR2014]', 
         '2015' = '2015 [YR2015]', 
         '2016' = '2016 [YR2016]', 
         '2017' = '2017 [YR2017]', 
         '2018' = '2018 [YR2018]', 
         '2019' = '2019 [YR2019]') %>%
  mutate(`2019` = as.numeric(`2019`)) 
```

```{r}
analysis<- Genderstatistics %>%
  filter(`Series Name` %in% c("Inflation, consumer prices (annual %)", "Population ages 15-64, female", "Population ages 15-64, male", "Life expectancy at birth, female (years)","Life expectancy at birth, male (years)")) %>%
  select(-c(`Series Code`,`Country Code`)) %>%
   pivot_longer(cols = -c(`Country Name`,`Series Name`),
               names_to = "Year",
               values_to = "count") %>%
  pivot_wider(names_from = "Series Name",
              values_from = "count") 
```

```{r}
analysis <- analysis %>%
mutate(Inflation = as.numeric(`Inflation, consumer prices (annual %)`)) %>%
  mutate(Population_ages_15_64_female = as.numeric(`Population ages 15-64, female`)) %>%
  mutate(Population_ages_15_64_male = as.numeric(`Population ages 15-64, male`)) %>%
  mutate(labour_force = `Population_ages_15_64_female`+`Population_ages_15_64_male`) %>%
  mutate(Year = as.numeric(Year)) %>%
  mutate(Life_expectancy_at_birth_female = as.numeric(`Life expectancy at birth, female (years)`))%>%
  mutate(Life_expectancy_at_birth_male = as.numeric(`Life expectancy at birth, male (years)`))%>%
  select(-c(`Inflation, consumer prices (annual %)`,`Population ages 15-64, female`,`Population ages 15-64, male`, `Life expectancy at birth, female (years)`, `Life expectancy at birth, male (years)`))
```

## Inflation

```{r A1, fig.cap = "Inflation vs Labour force" }
library(purrr)
library(ggplot2)
library(patchwork)
countries <- c("Colombia", "United States", "France", "Egypt, Arab Rep.")

infla_labour <- function(countries){
  p1 <- analysis %>%
  filter(`Country Name`== countries)%>%
    na.omit()%>%
    ggplot(aes(x=Year, y=Inflation)) +
  geom_line(color="#69b3a2", size=2) +
  scale_x_continuous(breaks = c(2011:2019))+
    scale_y_continuous(labels = scales::comma)+
  ggtitle("Inflation rate") +
    labs(title = countries)
  
   p2 <- analysis %>%
  filter(`Country Name`== countries)%>%
     na.omit()%>%
ggplot(aes(x=Year, y=labour_force)) +
  geom_line(color="grey",size=2) +
  scale_x_continuous(breaks = c(2011:2019))+
     scale_y_continuous(labels = scales::comma)+
  ggtitle("number of labour force") +
     labs(title = countries)

p1 + p2
}


Q1 <- map(countries, infla_labour)
print(Q1)
```
According to Figure\@ref(fig:A1), developed countries such as United States and France both have the lowest inflation rate in 2015. This is because in 2015, the crude oil price collapsed. (https://blogs.worldbank.org/developmenttalk/what-triggered-oil-price-plunge-2014-2016-and-why-it-failed-deliver-economic-impetus-eight-charts), and the global economy has not recovered from the GFC yet. ((https://www.reuters.com/article/us-usa-economy-inflation-idUSKCN0UY1LH)). 

Moreover, low inflation rate does not mean the currency is more valuable. On the contrary, it signals demand for goods and services is lower than expected and will then result in recession and the an increase in unemployment. (https://www.weforum.org/agenda/2019/06/inflation-is-healthy-for-the-economy-but-too-much-can-trigger-a-recession-7d37501704)

Additionally, developed countries usually have more stable inflation rate than developing countries. This is to keep the economy and the currency stable.

```{r A2}
library(kableExtra)
t1 <- analysis %>%
  select(`Country Name`,Year,Inflation,labour_force) %>%
  filter(Year == "2015") %>%
   knitr::kable(
    caption = "Inflation and the labour force in 2015"
  ) %>%
  kable_styling(c("hover", "striped"))

t1
```

Table \@ref(tab:A2) shows the 2015 inflation rate. 

## Gender distribution for labour force

Moreover, the labour force in each country is increasing but decreasing in France. We will take a deeper look in the employment and unemployment in the following sections and try to conclude why the labour force for France is decreasing. 

Let's also look at the gender distribution in the labour force.

```{r A3}
analysis %>%
  ggplot(aes(x = Year))+
  geom_line(aes(y = Population_ages_15_64_female), color = "red")+
  geom_line(aes(y = Population_ages_15_64_male), color = "green")+
  ylab("Gender distribution for labour force")+
  scale_x_continuous(breaks = c(2011:2019))+
  theme_light()+
  facet_wrap(~`Country Name`)
```

Figure\@ref(fig:A3) shows the lines for female labour force and the male labour force are almost overlapped with each other, meaning the gender distribution for labour force is fairly equal in these countries.


\clearpage
\section*{2}

#2 Nelson



\clearpage
\section*{3}

#3 Ratul

# Conclusion


